JCR-14-0358​ entitled ``Enemy at the Gates: Variation in Economic Growth from Civil Conflict''

### 2015-08-21 LaTeX/Revision/rev2.tex
edits to rev 2

\begin{itemize}
\item \textcolor{blue}{\emph{
	WOuld need to take into account distance of countries, hard to construct
	however, we have looked at other parameterizations such as mean distance
}}
\end{itemize}

@@

\begin{itemize}
\item \textcolor{blue}{\emph{
}}
\end{itemize}

@@

\begin{itemize}
\item \textcolor{blue}{\emph{
	When rerunning the model using the continuous variable each of the key results remain similar.
}}
\end{itemize}

>>>>

\begin{itemize}
\item \textcolor{blue}{\emph{
	We have looked at alternative parameterizations of the conflict distance measure including both the minimum and mean distances of conflicts to the respective nearest cities. Our results are robust across these parameterizations. We specifically chose not to create an aggregate conflict variable weighted by distance as we lacked theoretical justification for doing so given the argument advanced in the paper. If a country experiences both a rural and an urban conflict simultaneously, we do not expect the rural conflict to mitigate the economic consequences of the urban conflict. In the same way, we do not expect distant cities to compensate for the economic consequences felt by a city near conflict.
}}
\end{itemize}

@@

\begin{itemize}
\item \textcolor{blue}{\emph{
	We agree that this is an interesting hypothesis and would constitute a valuable extension to this research. However, we believe that this hypothesis is not a clear corollary to the arguments presented in this paper and deserves more consideration than a simple interaction term. Conflict area is not necessarily a proxy for conflict intensity and it is unclear to us that, controlling for intensity as we do, conflicts with larger areas that are nearer to cities will be of necessarily greater economic impact. In fact, one might argue that there is a dilution effect in which larger conflicts, controlling for intensity, produce less violence per square kilometer. Also, an interaction term like this supposes that there is a multiplicative effect such that \textnormal{conflict area} $\times$ \textnormal{conflict distance} is correlated with economic growth in a way that \textnormal{conflict area} $+$ \textnormal{conflict distance} is not. We reiterate that this is a very interesting avenue for further exploration but believe that we cannot address it adequately within the scope of this paper.
}}
\end{itemize}

@@

\begin{itemize}
\item \textcolor{blue}{\emph{
	When rerunning the model using the continuous variable each of the key results remain similar. We have used the continuous version of the variable in the revised draft.
}}
\end{itemize}
